Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-16 ind_files/01_Introduction.tex
Minor phrasing changes

\begin{itemize}
		\item Chapter \ref{chap_math_background} provides the necessary mathematical background and provides a toy example studying the size of a population of identical individuals that illustrates the major ideas used. If I am required to shoehorn the structure into the `intro-methods-results-discussion' format, then this chapter can be thought of as providing a mathematical `introduction' and illustration of the `methods' that will be used/generalized to get `results' in the following chapters.
		\item Chapter \ref{chap_BD} develops a formalism for describing the evolution of finite fluctuating populations that vary in one or more \emph{discrete} characters. This yields equations that generalize the classic Price equation and replicator-mutator equation to finite fluctuating populations.
		\item Chapter \ref{chap_infD_processes} extends the ideas developed in chapter \ref{chap_BD} to populations that vary in a single one-dimensional \emph{quantitative} character and derives a so-called `stochastic field theory' that describes evolution in such populations. This also results in some mathematical equations that may be of independent interest to physicists and applied mathematicians.
		\item Chapter \ref{chap_unification} provides a technical summary of the major results by deriving three important stochastic differential equations. These are equations for type frequencies, the population mean value of an arbitrary type-level quantity, and the population variance of an arbitrary type-level quantity, and respectively generalize the replicator-mutator equation, the Price equation, and \cite{lion_theoretical_2018}'s variance equation to finite, stochastically fluctuating populations. These equations predict a directional evolutionary force called `noise-induced selection' that is only seen in finite, fluctuating populations. Some implications for social evolution and community ecology are discussed. I also briefly discuss the field equation formalism I develop in chapter \ref{chap_infD_processes}.
		\item Chapter \ref{sec_disc} provides a quick summary of the major results and discusses biological implications, connections with previous studies, and opportunities for future work. This chapter has no equations (!). Thus, readers who do not want any mathematical equations can skip all other chapters and directly read chapter \ref{sec_disc} if they are interested only in the final results and takeaways\footnote{Though I promise I have tried my best to make sure the journey to this destination is also pleasant :)} 
\end{itemize}

>>>>

\begin{itemize}
		\item Chapter \ref{chap_math_background} provides the necessary mathematical background and provides a toy example studying the size of a population of identical individuals that illustrates the major ideas used. If I am required to shoehorn the structure into the `intro-methods-results-discussion' format, then this chapter can be thought of as providing a mathematical `introduction' and illustration of the `methods' that will be used/generalized to get `results' in the following chapters.
		\item Chapter \ref{chap_BD} develops a formalism for describing the evolution of finite fluctuating populations of individuals that come in arbitrarily many `types' which vary in a \emph{discrete} character. This yields equations that generalize the classic Price equation and replicator-mutator equation to finite fluctuating populations.
		\item Chapter \ref{chap_infD_processes} extends the ideas developed in chapter \ref{chap_BD} to populations that vary in a single one-dimensional \emph{quantitative} character and derives a so-called `stochastic field theory' that describes evolution in such populations. This also results in some mathematical equations that may be of independent interest to physicists and applied mathematicians.
		\item Chapter \ref{chap_unification} provides a technical summary of the major results by deriving three important stochastic differential equations. These are equations for type frequencies, the population mean value of an arbitrary type-level quantity, and the population variance of an arbitrary type-level quantity, and respectively generalize the replicator-mutator equation, the Price equation, and \cite{lion_theoretical_2018}'s variance equation to finite, stochastically fluctuating populations. These equations predict a directional evolutionary force called `noise-induced selection' that is only seen in finite, fluctuating populations. Some implications for social evolution and community ecology are discussed. I also briefly discuss the field equation formalism I develop in chapter \ref{chap_infD_processes}.
		\item Chapter \ref{sec_disc} provides a quick summary of the major results and discusses biological implications, connections with previous studies, and opportunities for future work. This chapter has no equations (!). Thus, readers who do not want any mathematical equations can skip all other chapters and directly read chapter \ref{sec_disc} if they are interested only in the final results and takeaways\footnote{Though I promise I have tried my best to make sure the journey to this destination is also pleasant :)} 
\end{itemize}
